A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-07 paper.tex
Revise Chap 4

The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts. To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest as well as the signature to brokers. Broker can first verify the signature from data provider with the public key on DID document. If it's valid, then the broker uploads the key, otherwise the process is aborted. Note that the broker need to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract. The key upload times is also restricted in order to avoid data provider uploading fake key frequently. If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds. Fig.~\ref{fig:key_upload} demonstrate the key upload to Product Contract via a broker.

@@

\subsubsection{Infrastructure}
In the following sections, we refer the low-level devices as \textbf{endpoint}s. MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic. The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth. The pub/sub model decouples publishers and subscribers in many ways:

@@

In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the whole E2EE process we present. The following section addresses the process.

@@

\subsubsection{Register Machine}
User with channel seed can acquire channel chain ownership. Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows tangle-accelerator to publish messages on MAM channel chain. Asymmetric encryption is utilizing during the process of exchanging Seed. Digital signature should be taken at the same time to ensure data integrity. Once seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator. Thus, seed isn't needed to be exposed during communication after an edge device is successfully registered.

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met a few challenges in the E2EE we proposed.

>>>>

The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts. To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest as well as the signature to brokers. Broker can first verify the signature from data provider with the public key on DID document. If it's valid, then the broker uploads the key, otherwise the process is aborted. Note that the broker need to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract. The key upload time is also restricted in order to avoid data provider uploading fake key frequently. If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds. Fig.~\ref{fig:key_upload} demonstrate the key upload to Product Contract via a broker.

@@

\subsubsection{Communication Protocol}
In the following sections, we refer the low-level devices as \textbf{endpoint}s. MQTT\cite{MQTT} is chosen as the communication protocol, which requires fewer TCP packets and less traffic. The topic-based pub/sub pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on endpoints with limited bandwidth. The pub/sub model decouples publishers and subscribers in many ways:

@@

In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:

@@

\subsubsection{Register with Tangle-accelerator}
User with channel seed can acquire channel chain ownership. Seed is generated by unique hardware information on edge device, so it should be transmitted to tangle-accelerator which allows it to publish messages on MAM channel chain. Asymmetric encryption is utilizing during the process of exchanging seed. Digital signature should be taken at the same time to ensure data integrity. Once the seed has been successfully exchanged, edge device is successfully registered on the specific tangle-accelerator. Thus, seed will not be exposed during communication after an edge device is successfully registered.

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, we met two challenges in the E2EE:
